Automatic Matching of Bullet Lands

### 2015-12-26 imaging-paper.Rnw
bootstrap for CIs

my.loess$fitted + ylab("Surface measurements")
@
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_resid} Residuals of loess fit for bullet~1-5. %Blue areas show pointwise 95\% confidence intervals.
}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
my.loess$resid + ylab("Residuals of loess Fit") 
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to bullet~1-5 (Barrel~1).}
\end{figure}
%
Figure~\ref{fig:loessfits} shows the signatures of all lands of bullet 2 (in grey) fired from the same barrel as bullet~1. The darker line overlaid on each of the signatures, shows signature from bullet~1-5. 
%We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from bullet~1-5. This is shown in Figure~\ref{fig:loessfits}. 
Bullet 2-1 is the best match for bullet~1-5, but the alignment is not quite  correct.

>>>>

my.loess$fitted + ylab("Surface measurements")
@
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_resid} Residuals of loess fit for bullet~1-5.
This defines the {\it signature} of bullet~1-5. Blue areas show  95\% bootstrap confidence intervals (based on $B=500$ bootstrap samples).
}
%<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
%my.loess$resid + ylab("Residuals of loess Fit") 
%@
<<boot_loess, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
boot.loess <- boot_fit_loess(br111_bullet, br111.groove)
poly <- with(boot.loess, data.frame(x = c(y,rev(y)), y=c(high, rev(low))))
qplot(x=x, y=y, geom="polygon", fill=I("steelblue"), data=poly) +
  geom_line(aes(x=y, y=resid), data=my.loess$data) +
  ylab("Residuals of loess fit") + xlab("y") + theme_bw()
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to bullet~1-5 (Barrel~1).}
\end{figure}
%
Figure~\ref{fig:loessfits} shows the signatures of all lands of bullet 2 (in grey) fired from the same barrel as bullet~1. The darker line overlaid on each of the signatures, shows signature from bullet~1-5. 
%We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from bullet~1-5. This is shown in Figure~\ref{fig:loessfits}. 
Bullet 2-1 is the best match for bullet~1-5, but the alignment is not quite  correct.
